Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-06-26 paper/structureScene.tex
comment on scattering and end-to-end learning

Adressing this task requires first to be able to capture meaningful aspects within the signal at small time scales. In other words, how do we represent an extract of the auditory scene signal over a sub-second interval? A standard tool for this are the mel-frequency cepstral coefficients (MFCCs), originally developed for speech processing \cite{davis-mermelstein}, but which have found wider use in recent years in music information retrieval \cite{logan} and environmental audio processing \cite{aucouturier2007bag}. A richer set of features are found in the scattering transform, a generic signal representation which has enjoyed significant success in various audio classification tasks \cite{Anden2014}.

>>>>

Adressing this task requires first to be able to capture meaningful aspects within the signal at small time scales. In other words, how do we represent an extract of the auditory scene signal over a sub-second interval? A standard tool for this are the mel-frequency cepstral coefficients (MFCCs), originally developed for speech processing \cite{davis-mermelstein}, but which have found wider use in recent years in music information retrieval \cite{logan} and environmental audio processing \cite{aucouturier2007bag}.
A richer set of features are found in the scattering transform, a generic signal representation which has enjoyed significant success in various audio classification tasks \cite{Anden2014}. This is because the scattering transform cascades wavelet convolutions and pointwise nonlinearities, thus imitating the architecture of a convolutional neural network.
As a result, the scattering transform benefits from some of the assets of end-to-end learning without needing a large amount of annotated training data to converge towards a meaningful representation.
